---
title: Sample Post 1
author: Yusuf Ansari
date: '2020-03-28'
slug: sample-post-1
categories: []
tags: [regex]
description: 'No Description'
topics: []
---





```{r}
#Load packages
pacman::p_load(tidyverse, stringr)
```

str_detect() is used to detect whether a string contains a certain pattern. At the most basic use of these functions, we can match strings of text. For instance
```{r}
jr1 = data.frame(sent = c("Theo is first", "Esther is second", "Colin - third"))
jr1
jr1 %>% filter(str_detect(sent, "Theo"))

jr = c("Theo is first", "Esther is second", "Colin - third")
str_detect(jr, "Theo")
str_detect(jr, "is")
```



So str_detect() will return TRUE when the element contains the pattern we searched for. If we want to return the actual strings that contain these patterns, we use str_subset()

```{r}
str_subset(jr, "Theo")
str_subset(jr, "is")
```


To practise our regex, we’ll need some text to practise on. Here we have a vector of filenames called files

```{r}
files = c(
  "tmp-project.csv", "project.csv", 
  "project2-csv-specs.csv", "project2.csv2.specs.xlsx", 
  "project_cars.ods", "project-houses.csv", 
  "Project_Trees.csv","project-cars.R",
  "project-houses.r", "project-final.xls", 
  "Project-final2.xlsx"
)
```



```{r}
str_subset(files, "\\.csv")
```




```{r}
str_subset(files, "^Proj")
```


```{r}
str_subset(files, "\\.csv$")
str_subset(files, "\\.ods$")
```


### Regex: Round parentheses,(), and the pipe, |

```{r}
str_subset(files, "\\.csv$|\\.ods$")
str_subset(files, "\\.(csv|ods)$")
```


### Regex: Square parentheses,[], and the asterisk, *
```{r}
str_extract(files, "[a-z]$")
str_subset(files, "[\\d]")
```



```{r}
str_extract(files, "[a-zA-Z]$")
```


Now, this is obviously useless at the moment. This is where does the asterisk comes into it. The asterisk is what is called a quantifier. There are three other quantifiers (+, ? and {}), but won’t cover them here. A quantifier quantifies how many of the characters we want to match and the asterisk means we want 0 or more characters of the same form. For instance, we could now extract all of the file extensions if we wished to

```{r}
str_extract(files, "[a-zA-Z]*$")
```



```{r}
str_subset(files, "[a-zA-Z]*\\.(csv|ods)$")
```



```{r}
str_subset(files, "(\\_|\\-)[a-zA-Z]*\\.(csv|ods)$")
```



```{r}
str_subset(files, "(P|p)roject(\\_|\\-)[a-zA-Z]*\\.(csv|ods)$")
str_subset(files, "^(P|p)roject(\\_|\\-)[a-zA-Z]*\\.(csv|ods)$")
```






















